%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

    \resumeProjectHeading
    {\textbf{Pitch Perfect} $|$ \emph{Java, HTML/CSS, JSoup, JavaScript, NLP API, AJAX, JDBC, MySQL, Git}}{}
    \resumeItemListStart
        \resumeItem{Designed and programmed a responsive web application and database, that helps discover sport activities and book facilities nearby.}
        \resumeItem{Integrated Servlets to process and aggregate third-party data for seamless operations of web service, boosting loading speed by \textbf{20\%}.}
    \resumeItemListEnd
    
    \resumeProjectHeading
    {\textbf{Financify} $|$ \emph{JavaScript, HTML/CSS, Figma, Git, MySQL}}{}
    \resumeItemListStart
        \resumeItem{As part of a team, I developed a mobile app soft-prototype, Financify, for diversifying investments, placed \textbf{1st} runner up in a pitch competition. Utilized AI/ML for stock price prediction and real estate investment analysis.}
        \resumeItem{Implemented a CRM platform for real estate management, improving communication and resolution of issues for tenants, property owners, and maintenance agencies.}
    \resumeItemListEnd
    
    \resumeProjectHeading
    {\textbf{RPS} $|$ \emph{Java, FXML, Figma, Git}}{}
    \resumeItemListStart
        \resumeItem{Developed a multi-threaded multiplayer game with GUI and communication protocols, resulting in a smooth and responsive gaming experience for players, with a performance increase of up to \textbf{50\%} by handling multiple tasks concurrently.}
        \resumeItem{Experience in designing and implementing a client-server architecture that enables efficient management of game state and communication between clients, resulting in scalable, high-performance, and secure applications.}
    \resumeItemListEnd
    
    \resumeProjectHeading
    {\textbf{SPFD} $|$ \emph{Python, Tkinter, Bash, FreeCAD, Fritzing, Ultimaker Cura}}{}
    \resumeItemListStart
        \resumeItem{ Prototyped and implemented a DIY Smart Pet Food Dispenser using a Raspberry Pi, with a automated weighing system that controls the amount of food and delivery intervals while enabling customization.}
        \resumeItem{Re-created enclosure within FreeCAD software featured with mounting holes, brackets and cable management for RPi that reduced model fitment errors by \textbf{40\%}.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Auto-Fill} $|$ \emph{Python, HTML/CSS, JavaScript, Selenium, PyQt, Git, Figma}}{}
    \resumeItemListStart
        \resumeItem{Designed and implemented a productivity application with a Graphical User Interface (GUI) that deals with Business Process Automation (BPA). It automates the process of manual data entry onto online submission forms.}
        \resumeItem{For scripting purposes Python and JavaScript was used. The User Interface was designed using PyQt (Python Plug-in). Selenium web framework was used for browser automation.}
    \resumeItemListEnd



\resumeSubHeadingListEnd
